Cooperative Decision Making for Communities of Autonomous Web Services

### 2013-12-17 proposal/presentation/ekpresentation/ehsan_presentation.tex
changes

    \begin{frame}{Cooperative Game Theory}
      \begin{itemize}
         \item Cooperative games are a branch of game theory that models cooperation or collaboration between agents.
         \begin{itemize}
            \item Cooperation to perform a set of tasks that requires different expertise.
            \item Agents do not have enough resource on their own to perform the tasks.
            \item Examples:
            \begin{itemize}
                \item Robots have the ability to move objects in a plant, but multiple robots are required to move a heavy box.
                \item Transportation domain: agents are trucks, trains, airplanes, ships... a task is a good to be transported.
            \end{itemize}
        \end{itemize}
        \item \textbf{Issues:}
            \begin{itemize}
                \item Coalition formation.
                \item Rewarding members when a task is completed.
            \end{itemize}
      \end{itemize}
    \end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame14 Background and Literature Review %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{The Classic Problem}
    We have a population $N$ of $n$ agents.
    \begin{definition} [Coalition]~\\
       A coalition $C$ is a set of agents: $C \in 2^N$.
        \begin{itemize}
            \item $N$ is the set of all agents (or players)
            \item $v:2^N \rightarrow R$ is the \emph{valuation function}. For $C \subseteq N$, $v(C)$ is the value obtained by the coalition $C$
        \end{itemize}
    \end{definition}

@@

%\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Some Properties of Valuation Functions}
    $\forall C_1,C_2 \subseteq N | C_1 \bigcap C_2 = \emptyset, i \in N, i \notin C_1$
    \begin{itemize}
        \item {\color{blue} Additive:} $v(C_1 \bigcup C_2) = v(C_1) + v(C_2)$
        \item {\color{blue} Super additive:} $v(C_1 \bigcup C_2) \geq v(C_1) + v(C_2)$ This is satisfied is many applications, or bigger coalitions will not form.
        \item {\color{blue} Weekly super additive:} $v(C_1 \bigcup \{i\}) \geq v(C_1) + v(\{i\})$
    \end{itemize}

    $\forall C_1,C_2 \subseteq N$
    \begin{itemize}
        \item {\color{blue} Convex:} $v(C_1 \bigcup C_2) \geq v(C_1) + v(C_2) - v(C_1 \bigcap C_2)$. Convexity has important properties in cooperative game theory solution concepts.
    \end{itemize}
    \begin{itemize}
        \item {\color{red} Subadditive:} $v(C_1 \bigcup C_2) \leq v(C_1) + v(C_2)$
    \end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Solution Properties}
    Let $x \in R^n$ be a solution of the coalition game $(N,v)$
    \begin{itemize}
        \item {\color{blue} Feasible solution:} $\sum_{i \in N} x(i) \leq v(N)$
        \item {\color{blue} Efficiency:} $x(N) = v(N)$
        \begin{itemize}
            \item the payoff distribution is an allocation of the entire worth of the grand coalition to all agents.
        \end{itemize}
        \item {\color{blue} Individual rationality:} $\forall i \in N, x(i) \geq v(\{i\})$
        \begin{itemize}
            \item player obtains at least its self-value of payoff.
        \end{itemize}
        \item {\color{blue} Group rationality:} $\forall C \subseteq N, \sum_{i \in N} x(i) \geq v(C)$
    \end{itemize}

@@

\begin{frame}{Problem Formulation and Modeling}
    \begin{itemize}
        \item Communities are robust service providers with well established market share and reputation.
        \item The community is characterized by a request rate $R_C$.
        \item Web services can perform tasks with some throughput rate ($Th_{ws}$).
        \item Web services come with different values of $QoS_{ws}$ for different metrics.
    \end{itemize}
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{$\epsilon$-Core}
    \begin{itemize}
        \item The core may not always be non-empty, core is a strong condition.
        \item $\epsilon$-core relaxes the core condition.
        \item $\forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S) - \epsilon$
        \item relative e-core: $\forall S \subseteq N, \sum_{x_i \in S} x_i \geq (1-\epsilon).v(S)$
    \end{itemize}
\end{frame}

>>>>

%    \begin{frame}{Cooperative Game Theory}
%      \begin{itemize}
%         \item Cooperative games are a branch of game theory that models cooperation or collaboration between agents.
%         \begin{itemize}
%            \item Cooperation to perform a set of tasks that requires different expertise.
%            \item Agents do not have enough resource on their own to perform the tasks.
%            \item Examples:
%            \begin{itemize}
%                \item Robots have the ability to move objects in a plant, but multiple robots are required to move a heavy box.
%                \item Transportation domain: agents are trucks, trains, airplanes, ships... a task is a good to be transported.
%            \end{itemize}
%        \end{itemize}
%        \item \textbf{Issues:}
%            \begin{itemize}
%                \item Coalition formation.
%                \item Rewarding members when a task is completed.
%            \end{itemize}
%      \end{itemize}
%    \end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame14 Background and Literature Review %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Cooperative Game Theory}
    \begin{itemize}
         \item Cooperative games are a branch of game theory that models cooperation or collaboration between agents within coalitions.
    \end{itemize}
    \begin{definition} [Coalition]~\\
       We have a population $N$ of $n$ agents, A coalition $C$ is a set of agents: $C \in 2^N$.
        \begin{itemize}
            \item $N$ is the set of all agents (or players)
            \item $v:2^N \rightarrow R$ is the \emph{valuation function}. For $C \subseteq N$, $v(C)$ is the value obtained by the coalition $C$
        \end{itemize}
    \end{definition}

@@

%\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Some Properties of Valuation Functions}
    $\forall C_1,C_2 \subseteq N | C_1 \bigcap C_2 = \emptyset, i \in N, i \notin C_1$
    \begin{itemize}
        \item {\color{blue} Additive:} $v(C_1 \bigcup C_2) = v(C_1) + v(C_2)$
        \item {\color{blue} Super additive:} $v(C_1 \bigcup C_2) \geq v(C_1) + v(C_2)$ This is satisfied is many applications, or bigger coalitions will not form.
        \item {\color{blue} Weekly super additive:} $v(C_1 \bigcup \{i\}) \geq v(C_1) + v(\{i\})$
        \item {\color{red} Subadditive:} $v(C_1 \bigcup C_2) \leq v(C_1) + v(C_2)$
    \end{itemize}

    $\forall C_1,C_2 \subseteq N$
    \begin{itemize}
        \item {\color{blue} Convex:} $v(C_1 \bigcup C_2) \geq v(C_1) + v(C_2) - v(C_1 \bigcap C_2)$. Convexity has important properties in cooperative game theory solution concepts.
    \end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Solution Properties}
    Let $x \in R^n$ be a solution of the coalition game $(N,v)$
    \begin{itemize}
        \item {\color{blue} Feasible solution:} $\sum_{i \in N} x(i) \leq v(N)$
        \item {\color{blue} Efficiency:} $\sum_{i \in N} x(i) = v(N)$
        \begin{itemize}
            \item the payoff distribution is an allocation of the entire worth of the grand coalition to all agents.
        \end{itemize}
        \item {\color{blue} Individual rationality:} $\forall i \in N, x(i) \geq v(\{i\})$
        \begin{itemize}
            \item player obtains at least its self-value of payoff.
        \end{itemize}
        \item {\color{blue} Group rationality:} $\forall C \subseteq N, \sum_{i \in N} x(i) \geq v(C)$
    \end{itemize}

@@

\begin{frame}{Problem Formulation and Modeling}
    \begin{itemize}
        \item Communities of web services are robust service providers with well established market share and reputation.
        \item The community is characterized by a request rate $R_C$.
        \item Web services can perform tasks with some throughput rate ($Th_{ws}$).
        \item Web services come with different values of $QoS_{ws}$ for different metrics.
    \end{itemize}
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{$\epsilon$-Core}
    \begin{itemize}
        \item The core may not always be non-empty, core is a strong condition.
        \item $\epsilon$-core relaxes the core condition.
        \item $\forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S) - \epsilon$
        \item relative $\epsilon$-Core: $\forall S \subseteq N, \sum_{x_i \in S} x_i \geq (1-\epsilon).v(S)$
    \end{itemize}
\end{frame}
